\documentclass[12pt,a4paper]{article}
\usepackage[nonumber]{cuisine}


\renewcommand*{\recipetitlefont}{\large\bfseries\sffamily}
\renewcommand*{\recipequantityfont}{\sffamily\bfseries}
\renewcommand*{\recipeunitfont}{\sffamily}
\renewcommand*{\recipeingredientfont}{\sffamily}
\renewcommand*{\recipefreeformfont}{\itshape}

\begin{document}
\begin{recipe}{Apple-Cinnamon Granola}{8--10 servings}{}
  \ingredient[1--2]{tsp}{coconut oil}
  Heat the over to 250\0F. Grease two baking sheets with the oil.
  \ingredient[4]{cups}{raw oat groats, soaked in water for 6 to 8 hours or overnight, then drained}
  \ingredient[1]{}{apple, cored and sliced}
  \ingredient[\fr12]{cup}{dried dried coconut flakes}
  \ingredient[2]{tsp}{ground cinnamon}
  \ingredient[2]{tbsp}{maple syrup or 1 tablespoon agave nectar}
  \ingredient[1]{tsp}{vanilla extract}
  \ingredient[\fr12]{tsp}{sea salt}
  Process the oats, apple, coconut, cinnamon, sweetener, vanilla and salt in a food processor for 30 seconds. Scrape sides, process for another 30 seconds and repeat one more time.
  \ingredient[\fr12]{cup}{raw almonds, chopped}
  \ingredient[\fr12]{cup}{pumpkin seeds, chopped}
  Transfer the mixture to a large mixing bowl and combine with the almonds and pumpkin seeds . Mix thoroughly with a spoon.
  \newstep
  Spread the mixture in a thin layer on the prepared baking sheets. Bake for 2 to 4 hours, turning the granola over a few times with a spatula until dried and crisp. You can set the oven temperature higher and reduce the baking time, but be sure to check frequently to avoid burning.
  \ingredient[\fr23]{cup}{raisins}
  Cool and stir in the raisins. Serve with non dairy milk and sliced banana or fresh berries. Keeps for 3 to 4 weeks in an airtight container.
\end{recipe}
\end{document}
